Considering scale in multilayer animal social networks

### 2020-06-16 paper/manuscript.Rmd
dates vs. window number

The ordinal multilayer network generated indicated within-year time windows of
increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
Edge overlap was higher in time windows 1, 6-11 and
15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). Time
windows of higher edge overlap, between approximately October and May, had
correspondingly higher graph strength compared to time windows of lower edge
overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
strength peaked across the time series in periods 9 and 10. These results
suggest that ordinal multilayer networks can effectively capture discrete time
windows of aggregation and dissaggregation related to resource availability, and
highlight the importance of carefully selecting the temporal scale of analysis.

>>>>

The ordinal multilayer network generated indicated within-year time windows of
increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
Edge overlap was higher in time windows 1, 6-11 and
15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
windows of higher edge overlap, between approximately October and May, had
correspondingly higher graph strength compared to time windows of lower edge
overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
strength peaked across the time series in periods 9 and 10. These results
suggest that ordinal multilayer networks can effectively capture discrete time
windows of aggregation and dissaggregation related to resource availability, and
highlight the importance of carefully selecting the temporal scale of analysis.
